### 2019-03-06 soc.tex
update preamble formatting

\documentclass[a4paper, 12pt]{article}
\usepackage[includefoot]{geometry}              % set margins

% LANGUAGE %
%-========-%
\usepackage{luavlna}                            % auto non-breaking spaces
\AtBeginDocument{\singlechars{czech}{AaIiVvOoUuSsZzKk}} % chars not to break on
\usepackage[czech]{babel}                       % use the czech language

% TOC AND LOF %
%-===========-%
\usepackage[subfigure, titles]{tocloft}         % controlling lof and lot
\usepackage[nottoc]{tocbibind}                  % no toc in toc

\makeatletter                                   % remove titles from lof and lot
\renewcommand\listoffigures{%
    \@mkboth{\MakeUppercase\listfigurename}%
        {\MakeUppercase\listfigurename}%
    \@starttoc{lof}%
}
\renewcommand\listoftables{%
    \@mkboth{\MakeUppercase\listtablename}%
        {\MakeUppercase\listtablename}%
    \@starttoc{lot}%
}
\makeatother

\setlength{\cftfigindent}{0pt}                  % no lof indentation
\setlength{\cfttabindent}{0pt}                  % no lot indentation

\renewcommand{\contentsname}{Obsah}             % change toc name

@@

% CODE %
%-====-%
\usepackage{minted}                             % uses python pygmentize

% GRAPHICS %
%-========-%
\usepackage{graphicx}                           % graphics package
\graphicspath{ {./img/} }                       % graphics path

\usepackage{float}                              % floats in correct position
\usepackage{subfig}                             % for subfigures

@@

\titlespacing{\section}      {0pt}{0pt}{6pt}    % 18pt (12pt + 6pt)
\titlespacing{\subsection}   {0pt}{0pt}{4pt}    % 16pt (12pt + 4pt)
\titlespacing{\subsubsection}{0pt}{0pt}{2pt}    % 14pt (12pt + 2pt)

@@

% BIBLIOGRAPHY %
%-============-%
\usepackage[backend=biber,
            style=iso-numeric,                  % numeric ISO 690
            sortlocale=cs_CZ,
            autolang=other,
            bibencoding=UTF8]{biblatex}         % use BibLaTeX for references
\addbibresource{soc.bib}                        % references file

\renewcommand*{\finentrypunct}{}                % don't end references with dot
\renewcommand{\multinamedelim}{\addcomma\space} % use comma as name delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim.
\renewbibmacro{in:}{}                           % don't use In: in references
\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap ref nums in sqr brackets

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting
\usepackage{multirow}                           % for creating multirow tables
\setlength\heavyrulewidth{0.2ex}                % inc top & bottomrule thickness

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}} % for table row stretching

% MATH %
%-====-%
\usepackage{amsmath, amstext}                   % math
\DeclareMathSymbol{.}{\mathord}{letters}{"3B}   % change dot in math to comma

@@

\glsaddall                                      % add all acronyms
\glssetwidest{WYSIWYGGG}                        % manually set the widest acr.

@@

\begin{document}
  % fixes some lines going to the margins
  \sloppy

@@

  % genereate toc
  \addtocontents{toc}{\vspace{-\cftaftertoctitleskip}\protect\setstretch{0.1}}
  \tableofcontents

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage[includefoot]{geometry} % for typesetting geometry

% LANGUAGE %
%-========-%
\usepackage{luavlna} % for auto non-breaking spaces
\AtBeginDocument{\singlechars{czech}{AaIiVvOoUuSsZzKk}} % chars not to break on

\usepackage[czech]{babel} % czech language localization

% TOC AND LOF %
%-===========-%
\usepackage[subfigure, titles]{tocloft} % controlling lof and lot
\usepackage[nottoc]{tocbibind} % remove reference to toc from toc

% remove titles from lof and lot, since they are grouped into one section
\makeatletter
\renewcommand\listoffigures{%
    \@mkboth{\MakeUppercase\listfigurename}%
        {\MakeUppercase\listfigurename}%
    \@starttoc{lof}%
}
\renewcommand\listoftables{%
    \@mkboth{\MakeUppercase\listtablename}%
        {\MakeUppercase\listtablename}%
    \@starttoc{lot}%
}
\makeatother

\setlength{\cftfigindent}{0pt} % remove lof indentation
\setlength{\cfttabindent}{0pt} % remove lot indentation

@@

% CODE %
%-====-%
\usepackage{minted} % highlight code with Pygments

% GRAPHICS %
%-========-%
\usepackage{graphicx}     % graphics package
\graphicspath{ {./img/} } % path to images

\usepackage{float} % floats in correct position (the [H] option)

\usepackage{subfig} % for subfigures

@@

\titlespacing{\section}      {0pt}{0pt}{6pt} % 18pt (12pt from parskip + 6pt)
\titlespacing{\subsection}   {0pt}{0pt}{4pt} % 16pt (12pt from parskip + 4pt)
\titlespacing{\subsubsection}{0pt}{0pt}{2pt} % 14pt (12pt from parskip + 2pt)

@@

% BIBLIOGRAPHY %
%-============-%
\usepackage[backend=biber,
            style=iso-numeric, % citations are in style [1], [2]...
            sortlocale=cs_CZ,
            autolang=other,
            bibencoding=UTF8]{biblatex} % use BibLaTeX for references

\addbibresource{soc.bib} % location of the references file

\renewcommand*{\finentrypunct}{} % don't end references with a dot
\renewcommand{\multinamedelim}{\addcomma\space} % use comma as name delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % "a" between the last 2 names
\renewbibmacro{in:}{} % don't use In: in references
\DeclareFieldFormat{labelnumberwidth}{[#1]} % wrap reference numbers in square brackets

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop} % table caption on top
\restylefloat{table}  % -||-

\usepackage{booktabs} % table formatting

\usepackage{multirow}            % for creating multirow tables
\setlength\heavyrulewidth{0.2ex} % increase top and bottom rule thicknesses

@@

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}} % table row stretching

% MATH %
%-====-%
\usepackage{amsmath, amstext} % for typesetting math
\DeclareMathSymbol{.}{\mathord}{letters}{"3B} % change dot in math to a comma

@@

\glsaddall % add all acronyms

% For setting the list of acronyms alignment (note the two extra G's). I didn't
% find a better way to increase the spacing between the acronym and its
% description in the "Seznam zkratek" section, since \glsfindwidesttoplevelname
% only inserts one space.
\glssetwidest{WYSIWYGGG}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% D O C U M E N T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
  \sloppy % fixes some lines going to the margins

@@

  % Makes the spacing between toc heading and the contents the same as other
  % section and also makes the item spacing smaller
  \addtocontents{toc}{\vspace{-\cftaftertoctitleskip}\protect\setstretch{0.1}}

  % genereate toc
  \tableofcontents
